%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jameson Zeller} \\ \vspace{1pt}
    Round Lake, Illinois \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 773-647-7679 ~ \href{mailto:jz@jamesonzeller.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{jz@jamesonzeller.com}} ~ 
    \href{https://linkedin.com/in/jameson-zeller/}{\raisebox{-0.2\height}\faGlobe\ \underline{jamesonzeller.com}}  ~
    \href{https://github.com/imjamesonzeller}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/imjamesonzeller}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Aug. 2024 -- May 2028}
      {Bachelor of Science in Mathematics \& Computer Science; Minor in Business}{Champaign, Illinois}
      \resumeItemListStart
        \resumeItem{\textbf{3.87 GPA}; Elsie Thomas Fraser Award Winner; Dean's List; Habitat for Humanity}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RELEVANT COURSEWORK-----------
% \section{Relevant Coursework}
% \begin{itemize}[leftmargin=0.15in, itemsep=2pt]
%   \item Data Structures \& Algorithms, Introduction to Programming (Kotlin \& C++), Computer Architecture
% \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
  {Hudl}{May 2026 -- Aug. 2026}
  {Software Engineering Intern}{Lincoln, NE}
  \resumeItemListStart
    \resumeItem{Anticipated work in C\#, .NET, and React.}
  \resumeItemListEnd

  \resumeSubheading
    {AthXcel (acquired by Optima Sports Group - Jan. 2026)}{May 2025 -- Present}
    {Product Manager}{Remote / Round Lake, IL}
    \resumeItemListStart
      \resumeItem{Architected and deployed "Coach Eddie" AI Chat system using \textbf{C\# .NET} backend with \textbf{TypeScript React} frontend, serving as an in-app assistant for training guidance and user support across pilot user base.}
      \resumeItem{Designed and implemented tool call hanlder and registry framework, enabling type-safe, extensible function routing and orchestration of integrations with \textbf{OpenAI}, achieving dynamic intent-to-action mapping.}
      \resumeItem{Engineered full-stack solution including database schema design in \textbf{SQL Server}, conversation management system, internal testing tools, and deployment in \textbf{Azure Functions} and \textbf{App Services}.}
      \resumeItem{Led cross-company integration efforts post-acquisition, coordinating engineering teams from AthXcel and Optima Sports Group to design API contracts and unify systems, ensuring seamless data exchange.}
      \resumeItem{Own product roadmap and prioritization, aligning engineering, design, and leadership teams with business goals.}
    \resumeItemListEnd

    % \resumeSubSubheading{Software Engineer Intern}{May 2024 -- Aug. 2024}
    \vspace{-16pt}
    \resumeProjectHeading
    {\emph{Software Engineering Intern}}{May 2025 -- Aug. 2025}
    \resumeItemListStart
      \resumeItem{Optimized \textbf{OpenAI}-powered prompt design, reducing token usage by \textbf{25\%+} and cutting API costs.}
\resumeItem{Designed and architected end-to-end video analysis system, defining technical requirements, database schemas, and API contracts to enable athletes and coaches to review training footage.}
    \resumeItemListEnd

  \resumeSubheading
    {Siebel School of Computing and Data Science}{Jan. 2025 -- Present}
    {CS 124 Tutor (\textbf{Java} / \textbf{Kotlin})}{Champaign, IL}
    \resumeItemListStart
      \resumeItem{Mentor students in UIUC's CS 124 programming course, simplifying complex design and debugging concepts to build students' technical confidence.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP / EXTRACURRICULAR-----------
\section{Leadership}
\resumeSubHeadingListStart
  \resumeSubheading
    {Buona Beef}{June 2022 -- Aug. 2024}
    {Guest Service Trainer}{Lakemoor, IL}
    \resumeItemListStart
      \resumeItem{Coached 100+ new employees on company policies, customer interaction, and restaurant procedures.}
      \resumeItem{Assisted with the grand opening of 3 new store locations in collaboration with the corporate team.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
  {\textbf{\href{https://github.com/imjamesonzeller/tasklight-v3}{Tasklight}} \emph{(macOS Productivity App)}}{2025}  \resumeItemListStart
    \resumeItem{Developed a Spotlight-style task capture app using \textbf{Go} and \textbf{React} (Wails) to instantly log tasks to Notion.}
    \resumeItem{Built a companion API service in \textbf{Spring Boot} that proxies requests to \textbf{OpenAI}, letting users either supply their own API key or use a quota-limited shared key managed by me.}
    \resumeItem{Integrated Notion OAuth, Apple Keychain token storage, global keyboard shortcuts, and \textbf{OpenAI}-powered NLP.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{\href{https://github.com/imjamesonzeller/api}{Self-Hosted APIs}} \emph{(Spring Boot \& Flask Services)}}{2025}
  \resumeItemListStart
    \resumeItem{Developed a suite of custom APIs in \textbf{Kotlin (Spring Boot)} and \textbf{Python (Flask)} for personal productivity and hobby projects.}
    \resumeItem{Containerized services with \textbf{Docker}, deployed to a self-hosted \textbf{TrueNAS} server, and exposed securely through \textbf{Cloudflare Tunnels}.}
    \resumeItem{Applied best practices including idempotent design, OAuth/Keychain security, quota management, and unit tests with JUnit \& MockMvc.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Kotlin / Java, C\#, Python, C++, SQL, TypeScript, Go} \\
    \textbf{Frameworks \& Tools}{: Spring Boot, .NET, Cloudflare R2 (AWS S3 SDK), Azure, React, Docker, Git, Flask, Jira} \\
  }}
\end{itemize}

\end{document}